---
title: "sensitivity_analysis"
author: "Ryan Yan"
date: "2023-02-14"
output: html_document
---

Code for Yan, Y., Hunt, L. T., & Hassall, C. D. (2023). Reward positivity biases interval production in a continuous timing task. bioRxiv, 2023-07.

Contact: Ryan Yan, Department of Psychology, Stanford University, ryany98@stanford.edu

*Examines whether the results for the linear mixed model still holds with different data exclusion criteria.*

```{r}
num_practice_block <- 0
ci <- c(0.005,0.995)
exclude_method = "quantile"
```

# read in csv files and demographic info

```{r read files}
window_type = "meta" #"50peak"
file_ERP <- read.csv(paste0(dataset_path,'R/rERP_meta.csv'))
file_tbt_raw <- read.csv(paste0(dataset_path,'R/tbt_',window_type,'.csv')) #tbt_meta.csv
```

# tbt preprocessing

## (1) calculate RT adjustment and local mean; (2) recode some categorical variables; (3) add in location-in-chunk

```{r preprocessing,echo=FALSE}
#calculate local mean and rt adjustment
file_tbt_raw <- merge(file_demo,file_tbt_raw, by = "participant_ID")

# add in text variables of tempo and outcome
file_tbt_raw$tempo <- NA
file_tbt_raw$tempo[which(file_tbt_raw$blockType <= 4)] <- "fast"
file_tbt_raw$tempo[which(file_tbt_raw$blockType >=9)] <- "slow"
file_tbt_raw$tempo[which(file_tbt_raw$blockType >= 5 & file_tbt_raw$blockType <= 8)] <- "medium"

file_tbt_raw$feedback <- NA
file_tbt_raw$feedback[which(file_tbt_raw$outcome == 0)] <- "early"
file_tbt_raw$feedback[which(file_tbt_raw$outcome == 1)] <- "on_time"
file_tbt_raw$feedback[which(file_tbt_raw$outcome == 2)] <- "late"

file_tbt_raw$feedback_dich <- NA
file_tbt_raw$feedback_dich[which(file_tbt_raw$outcome != 1)] <- 0
file_tbt_raw$feedback_dich[which(file_tbt_raw$outcome == 1)] <- 1

# add in hand and pattern
pattern1_list <- c(1,2,5,6,9,10)
pattern2_list <- c(3,4,7,8,11,12)
right_list <- c(2,4,6,8,10,12)
left_list <- c(1,3,5,7,9,11)

file_tbt_raw$pattern <- NA
file_tbt_raw$main_hand <- NA

file_tbt_raw$pattern[file_tbt_raw$blockType %in% pattern1_list] <- "pattern1"
file_tbt_raw$pattern[file_tbt_raw$blockType %in% pattern2_list] <- "pattern2"

file_tbt_raw$main_hand[file_tbt_raw$blockType %in% right_list] <- "right"
file_tbt_raw$main_hand[file_tbt_raw$blockType %in% left_list] <- "left"

#add in chunking var
file_tbt_raw$chunk_location <- NA
file_tbt_raw <- file_tbt_raw%>%
  rowwise()%>%
  mutate(chunk_location = ifelse(pattern == "pattern1",(trialLoop_thisRepN)%%4, #00,01,02,03
         ifelse(pattern == "pattern2",10+(trialLoop_thisRepN)%%6,NA)))#10,11,12,13,14,15

file_tbt_raw <- file_tbt_raw%>%
  mutate(chunk_location = ifelse(chunk_location %in% c(0,1,2,3),paste0("A",chunk_location),
                                  ifelse(chunk_location %in% c(10,11,12,13,14,15),paste0("B",(chunk_location-10)),NA)))

file_tbt_raw$chunk_location <- as.factor(file_tbt_raw$chunk_location)

file_tbt_raw <- file_tbt_raw %>%
  group_by(participant_ID,blockLoop_thisRepN)%>% 
  mutate(target_interval = ifelse(tempo == "fast",0.4,
                                  ifelse(tempo == "medium",0.6,
                                         ifelse(tempo == "slow",1))),
         last_rt = lag(trialResp_rt,1),
         rt_adjustment = trialResp_rt - last_rt,
         last_rt_adjustment = lag(rt_adjustment,1), #this is for lag-1 model
         last_RewP = lag(rERPRewp,1),#this is for lag+1 model
         last_feedback = lag(feedback,1),
         last_feedback_dich = lag(feedback_dich,1),
         last_last_RewP = lag(last_RewP,1),#this is for lag+2 model
         last_last_last_RewP = lag(last_last_RewP,1),#this is for lag+2 model
         rt_mean10 = rollmean(trialResp_rt, k = 10, fill = NA, align = "right"),
         rt_deviance_mean10 = ifelse(!is.na(rt_mean10),trialResp_rt - rt_mean10,
                                     trialResp_rt - target_interval),
         last_rt_deviance_mean10 = lag(rt_deviance_mean10,1),
         last_last_rt_deviance_mean10 = lag(last_rt_deviance_mean10,1),
         last_chunk_location = lag(chunk_location,1))
```

## exclude practice blocks
```{r}
range(file_tbt_raw$trialResp_rt,na.rm = TRUE)
range(file_tbt_raw$rt_adjustment,na.rm = TRUE)
range(file_tbt_raw$rERPRewp[file_tbt_raw$rERPRewp != -99],na.rm = TRUE)
range(file_tbt_raw$last_rt_deviance_mean10,na.rm = TRUE)

file_tbt_raw <- file_tbt_raw%>%filter(blockLoop_thisRepN >= num_practice_block, trialResp_corr == 1)
```

## excluding outliers on both end (1~99 percentile).
```{r data cleaning, include=FALSE}
if (exclude_method == "quantile"){
  
  # rt outliers (needs log transformation)
  tbt_outlier <-exp(c(log(quantile(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "fast")], ci)),
                  log(quantile(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "medium")], ci)),
                  log(quantile(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "slow")], ci))))


  #RT adjustment outliers
  rtAdj_outlier <-quantile(file_tbt_raw$rt_adjustment, ci,na.rm = TRUE)


  #RT deviation outliers
  rtDev_outlier <-quantile(file_tbt_raw$last_rt_deviance_mean10, ci,na.rm = TRUE)


  # ERP artifacts
  file_tbt_raw$eeg_include = 0
  rtEEG_outlier <- quantile(file_tbt_raw$rERPRewp[which(file_tbt_raw$erpRewp != -99,
                                                        file_tbt_raw$rERPRewp!=-99)], ci,na.rm = TRUE)

  } else if (exclude_method == "std"){
    times = 4
    # rt outlier (log transformation)
  tbt_outlier <-exp(c(mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "fast")]))-times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "fast")])),
                  mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "fast")]))+times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "fast")])),
                  mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "medium")]))-times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "medium")])),
                  mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "medium")]))+times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "medium")])),
                  mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "slow")]))-times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "slow")])),
                  mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "slow")]))+times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "slow")]))
                  ))
  
  rtAdj_outlier <- c(mean(file_tbt_raw$rt_adjustment,na.rm = TRUE)-times*sd(file_tbt_raw$rt_adjustment,na.rm = TRUE),
                  mean(file_tbt_raw$rt_adjustment,na.rm = TRUE)+times*sd(file_tbt_raw$rt_adjustment,na.rm = TRUE))
   
  #RT deviation outliers
  rtDev_outlier <-   c(mean(file_tbt_raw$last_rt_deviance_mean10,na.rm = TRUE)-times*sd(file_tbt_raw$last_rt_deviance_mean10,na.rm = TRUE),
                  mean(file_tbt_raw$last_rt_deviance_mean10,na.rm = TRUE)+times*sd(file_tbt_raw$last_rt_deviance_mean10,na.rm = TRUE))


  # ERP artifacts

  rtEEG_outlier <- c(mean(file_tbt_raw$rERPRewp[which(file_tbt_raw$erpRewp != -99,
                                                        file_tbt_raw$rERPRewp!=-99)],na.rm = TRUE)-times*sd(file_tbt_raw$rERPRewp[which(file_tbt_raw$erpRewp != -99,
                                                        file_tbt_raw$rERPRewp!=-99)],na.rm = TRUE),
                  mean(file_tbt_raw$rERPRewp[which(file_tbt_raw$erpRewp != -99,
                                                        file_tbt_raw$rERPRewp!=-99)],na.rm = TRUE)+times*sd(file_tbt_raw$rERPRewp[which(file_tbt_raw$erpRewp != -99,
                                                        file_tbt_raw$rERPRewp!=-99)],na.rm = TRUE))
}

```

## exclude the outliers as specified above
```{r}
print(paste0(c("rt lower boundary: ","rt upper boundary: "),tbt_outlier))
print(paste0(c("rt adjustment lower boundary: ","rt adjustment upper boundary: "),rtAdj_outlier))
print(paste0(c("rt deviation lower boundary: ","rt deviation upper boundary: "),rtDev_outlier))
```

### exclude for file_tbt_raw
```{r include = FALSE}
file_tbt_raw$rt_include = 0
file_tbt_raw$rt_include[which(file_tbt_raw$tempo == "fast" & file_tbt_raw$trialResp_rt >= tbt_outlier[1] &
                                file_tbt_raw$trialResp_rt <= tbt_outlier[2] & file_tbt_raw$trialResp_corr == 1)] <- 1
file_tbt_raw$rt_include[which(file_tbt_raw$tempo == "medium" & file_tbt_raw$trialResp_rt >= tbt_outlier[3] &
                                file_tbt_raw$trialResp_rt <= tbt_outlier[4] & file_tbt_raw$trialResp_corr == 1)] <- 1
file_tbt_raw$rt_include[which(file_tbt_raw$tempo == "slow" & file_tbt_raw$trialResp_rt >= tbt_outlier[5] &
                                file_tbt_raw$trialResp_rt <= tbt_outlier[6] & file_tbt_raw$trialResp_corr == 1)] <- 1

file_tbt_raw$rtAdj_include = 0
file_tbt_raw$rtAdj_include[which(file_tbt_raw$rt_adjustment >= rtAdj_outlier[1] &
                                     file_tbt_raw$rt_adjustment <= rtAdj_outlier[2])] <- 1
 file_tbt_raw$rtDev_include = 0
file_tbt_raw$rtDev_include[which((file_tbt_raw$last_rt_deviance_mean10 >= rtDev_outlier[1] &
                                     file_tbt_raw$last_rt_deviance_mean10 <= rtDev_outlier[2])| file_tbt_raw$trialLoop_thisRepN < 9)] <- 1
file_tbt_raw$eeg_include = 0
file_tbt_raw$eeg_include[which(file_tbt_raw$erpRewp != -99 & file_tbt_raw$rERPRewp !=-99 &
                                   file_tbt_raw$rERPRewp > rtEEG_outlier[1] & file_tbt_raw$rERPRewp < rtEEG_outlier[2])] <- 1
```

```{r data exclusion}
table(file_tbt_raw$rt_include)/sum(file_tbt_raw$rt_include)
table(file_tbt_raw$rtAdj_include)/sum(file_tbt_raw$rtAdj_include)
table(file_tbt_raw$rtDev_include)/sum(file_tbt_raw$rtDev_include)
table(file_tbt_raw$eeg_include)/sum(file_tbt_raw$eeg_include)

file_tbt_raw$include <- as.numeric(file_tbt_raw$rt_include == 1 & file_tbt_raw$rtAdj_include==1 & file_tbt_raw$eeg_include==1 & file_tbt_raw$rtDev_include == 1)

count(file_tbt_raw%>%ungroup,include)

print(paste0("Inclusion rate = ",length(which(file_tbt_raw$include == 1))/length(which(file_tbt_raw$rERPRewp != -99))))

file_tbt <- file_tbt_raw%>%filter(include == 1)

range(file_tbt$trialResp_rt,na.rm = TRUE)
range(file_tbt$rt_adjustment,na.rm = TRUE)
range(file_tbt$rERPRewp,na.rm = TRUE)
range(file_tbt$last_rt_deviance_mean10,na.rm = TRUE)
```

# trial-by-trial EEG predicting RT adjustments
```{r}
file_tbt$feedback <- factor(file_tbt$feedback, levels = c("on_time","early","late"))
file_tbt$tempo <- factor(file_tbt$tempo, levels = c("slow","medium","fast"))
```

```{r}
lm1 <-  lmer(rt_adjustment ~ rERPRewp * tempo * feedback + chunk_location + last_rt_deviance_mean10* tempo +(1|participant_ID), data= file_tbt)
```

```{r}
summary_lm1 <- summary(lm1)
summary_lm1

lme.dscore(lm1,file_tbt,type = "lme4")

summary(lmer(rt_adjustment ~ rERPRewp * tempo * feedback + (1|participant_ID), data= file_tbt))
```
