---
title: "analysis_09a_tbt_preprocessing"
author: "Ryan Yan"
date: "2023-07-06"
output: html_document
---

Code for Yan, Y., Hunt, L. T., & Hassall, C. D. (2023). Reward positivity biases interval production in a continuous timing task. bioRxiv, 2023-07.

Contact: Ryan Yan, Department of Psychology, Stanford University, ryany98@stanford.edu

# set up library and format
```{r}
rm(list = ls())
```

```{r setup, include=FALSE}
library(tidyverse)
library(zoo)
library(ggplot2)
library(ggpubr)
library(emmeans)
library(lme4)
library(sjPlot)
library(brms)
library(grid)
library(sjPlot)
library(MuMIn)
library(r2glmm)
library(bayestestR)
library(lmerTest)
library(patchwork)
library(car)
library(effects)
library(rstatix)
library(ggcorrplot2)
library(grid)
library(gridExtra)
library(extrafont)
library(EMAtools)
library(afex)
library(effectsize)
library(kableExtra)
library(ggeffects)
library(fdrtool)
# if (!requireNamespace("devtools")) install.packages("devtools")
```

```{r}
theme_set(theme_classic()+
          theme(text = element_text(family = "Helvetica", size = 12)))

purpleOrange_palette3 = c("purple4","plum3","gold") # the feedback palette (gold = on time)
greys_palette3 = c("bisque3","bisque4","black") # the tempo palette (black = slow)
```

# set up preprocessing params

```{r}
num_practice_block <- 3 #first 3 blocks dropped as practice rounds

exclude_method = "quantile"
ci <- c(0.01,0.99) #exclude top and bottom 1%
```

# read in csv files

```{r read files}
dataset_path = "/Users/rh/Documents/ds004152/" # change this to your local address
window_type = "meta" #"50peak"; this is the method for getting the RewP window. "meta" means it's from a previous analysis (Sambrook and Goslin 2015)
file_ERP <- read.csv(paste0(dataset_path,paste0('R/rERP_',window_type,'.csv')))
file_traditional_ERP <- read.csv(paste0(dataset_path,'R/traditional_ERP_',window_type,'.csv'))
file_tbt_raw_orig <- read.csv(paste0(dataset_path,'R/tbt_',window_type,'.csv'))
file_demo <- read.table(paste0(dataset_path,'/participants.tsv'))%>%
  rename(participant_ID = participant_id)
```

# tbt preprocessing

(1) calculate RT adjustment and local mean; 
(2) recode some categorical variables; 
(3) add in location-in-chunk to control for chunking effect

```{r preprocessing,echo=FALSE}
#calculate local mean and rt adjustment
file_tbt_raw_orig <- merge(file_demo,file_tbt_raw_orig, by = "participant_ID")

# add in text variables of tempo and outcome
file_tbt_raw_orig$tempo <- NA
file_tbt_raw_orig$tempo[which(file_tbt_raw_orig$blockType <= 4)] <- "fast"
file_tbt_raw_orig$tempo[which(file_tbt_raw_orig$blockType >=9)] <- "slow"
file_tbt_raw_orig$tempo[which(file_tbt_raw_orig$blockType >= 5 & file_tbt_raw_orig$blockType <= 8)] <- "medium"

file_tbt_raw_orig$feedback <- NA
file_tbt_raw_orig$feedback[which(file_tbt_raw_orig$outcome == 0)] <- "early"
file_tbt_raw_orig$feedback[which(file_tbt_raw_orig$outcome == 1)] <- "on_time"
file_tbt_raw_orig$feedback[which(file_tbt_raw_orig$outcome == 2)] <- "late"

file_tbt_raw_orig$feedback_dich <- NA
file_tbt_raw_orig$feedback_dich[which(file_tbt_raw_orig$outcome != 1)] <- 0
file_tbt_raw_orig$feedback_dich[which(file_tbt_raw_orig$outcome == 1)] <- 1

# add in hand and pattern
pattern1_list <- c(1,2,5,6,9,10)
pattern2_list <- c(3,4,7,8,11,12)
right_list <- c(2,4,6,8,10,12)
left_list <- c(1,3,5,7,9,11)

file_tbt_raw_orig$pattern <- NA
file_tbt_raw_orig$main_hand <- NA

file_tbt_raw_orig$pattern[file_tbt_raw_orig$blockType %in% pattern1_list] <- "pattern1"
file_tbt_raw_orig$pattern[file_tbt_raw_orig$blockType %in% pattern2_list] <- "pattern2"

file_tbt_raw_orig$main_hand[file_tbt_raw_orig$blockType %in% right_list] <- "right"
file_tbt_raw_orig$main_hand[file_tbt_raw_orig$blockType %in% left_list] <- "left"

#add in chunking variable
file_tbt_raw_orig$chunk_location <- NA
file_tbt_raw_orig <- file_tbt_raw_orig%>%
  rowwise()%>%
  mutate(chunk_location = ifelse(pattern == "pattern1",(trialLoop_thisRepN)%%4, #00,01,02,03
         ifelse(pattern == "pattern2",10+(trialLoop_thisRepN)%%6,NA)))#10,11,12,13,14,15

file_tbt_raw_orig <- file_tbt_raw_orig%>%
  mutate(chunk_location = ifelse(chunk_location %in% c(0,1,2,3),paste0("A",chunk_location),
                                  ifelse(chunk_location %in% c(10,11,12,13,14,15),paste0("B",(chunk_location-10)),NA)))

file_tbt_raw_orig$chunk_location <- as.factor(file_tbt_raw_orig$chunk_location)
  
file_tbt_raw_orig <- file_tbt_raw_orig %>%
  group_by(participant_ID,blockLoop_thisRepN)%>% 
  mutate(target_interval = ifelse(tempo == "fast",0.4,
                                  ifelse(tempo == "medium",0.6,
                                         ifelse(tempo == "slow",1))),
         last_rt = lag(trialResp_rt,1),
         rt_adjustment = trialResp_rt - last_rt,
         last_rt_adjustment = lag(rt_adjustment,1), #this is for lag-1 model
         last_RewP = lag(rERPRewp,1),#this is for lag+1 model
         last_feedback = lag(feedback,1),
         last_feedback_dich = lag(feedback_dich,1),
         last_last_RewP = lag(last_RewP,1),#this is for lag+2 model
         last_last_last_RewP = lag(last_last_RewP,1),#this is for lag+2 model
         rt_mean10 = rollmean(trialResp_rt, k = 10, fill = NA, align = "right"),
         rt_deviance_mean10 = ifelse(!is.na(rt_mean10),trialResp_rt - rt_mean10,
                                     trialResp_rt - target_interval),
         last_rt_deviance_mean10 = lag(rt_deviance_mean10,1),
         last_last_rt_deviance_mean10 = lag(last_rt_deviance_mean10,1),
         last_chunk_location = lag(chunk_location,1))
```

# generate a vector differentiating below or above mean RT adjustment, for analysis_07_mediansplit.m
```{r echo = FALSE}
rt_adjust_mean_summary <- file_tbt_raw_orig%>%
  group_by(tempo,feedback,participant_ID)%>%
  summarise(mean_rt_adjust = mean(rt_adjustment,na.rm = TRUE),
            mean_rt = mean(trialResp_rt, na.rm = TRUE))

file_tbt_lab <- left_join(file_tbt_raw_orig,rt_adjust_mean_summary,by = c("tempo","feedback","participant_ID"))%>%
  mutate(rt_adjust_cat = as.numeric(rt_adjustment >= mean_rt_adjust),
         rt_cat = as.numeric(trialResp_rt >= mean_rt))

write.csv(file_tbt_lab%>%
  select(participant_ID,blockLoop_thisRepN,trialLoop_thisRepN,rt_adjust_cat,rt_cat),
  'data_files/rt_vector.csv')
```

## exclude practice blocks
```{r}
range(file_tbt_raw_orig$trialResp_rt,na.rm = TRUE)
range(file_tbt_raw_orig$rt_adjustment,na.rm = TRUE)
range(file_tbt_raw_orig$rERPRewp[file_tbt_raw_orig$rERPRewp != -99],na.rm = TRUE)
range(file_tbt_raw_orig$last_rt_deviance_mean10,na.rm = TRUE)

file_tbt_raw <- file_tbt_raw_orig%>%filter(blockLoop_thisRepN >= num_practice_block, trialResp_corr == 1)
```

## create variable that count the recent on-time rate (for analysis_12_contextual_modulation.rmd)
```{r include = F}
file_timecourse <- file_tbt_raw%>%
  group_by(participant_ID,blockLoop_thisRepN)%>%
  mutate(recent_avg_winpercent1 = lag(rollmean(feedback_dich, 1, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent2 = lag(rollmean(feedback_dich, 2, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent3 = lag(rollmean(feedback_dich, 3, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent4 = lag(rollmean(feedback_dich, 4, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent5 = lag(rollmean(feedback_dich, 5, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent6 = lag(rollmean(feedback_dich, 6, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent7 = lag(rollmean(feedback_dich, 7, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent8 = lag(rollmean(feedback_dich, 8, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent9 = lag(rollmean(feedback_dich, 9, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent10 = lag(rollmean(feedback_dich, 10, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent11 = lag(rollmean(feedback_dich, 11, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent12 = lag(rollmean(feedback_dich, 12, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent13 = lag(rollmean(feedback_dich, 13, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent14 = lag(rollmean(feedback_dich, 14, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent15 = lag(rollmean(feedback_dich, 15, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent16 = lag(rollmean(feedback_dich, 16, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent17 = lag(rollmean(feedback_dich, 17, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent18 = lag(rollmean(feedback_dich, 18, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent19 = lag(rollmean(feedback_dich, 19, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent20 = lag(rollmean(feedback_dich, 20, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent21 = lag(rollmean(feedback_dich, 21, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent22 = lag(rollmean(feedback_dich, 22, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent23 = lag(rollmean(feedback_dich, 23, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent24 = lag(rollmean(feedback_dich, 24, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent25 = lag(rollmean(feedback_dich, 25, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent26 = lag(rollmean(feedback_dich, 26, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent27 = lag(rollmean(feedback_dich, 27, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent28 = lag(rollmean(feedback_dich, 28, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent29 = lag(rollmean(feedback_dich, 29, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent30 = lag(rollmean(feedback_dich, 30, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent31 = lag(rollmean(feedback_dich, 31, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent32 = lag(rollmean(feedback_dich, 32, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent33 = lag(rollmean(feedback_dich, 33, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent34 = lag(rollmean(feedback_dich, 34, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent35 = lag(rollmean(feedback_dich, 35, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent36 = lag(rollmean(feedback_dich, 36, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent37 = lag(rollmean(feedback_dich, 37, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent38 = lag(rollmean(feedback_dich, 38, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent39 = lag(rollmean(feedback_dich, 39, na.pad = TRUE, align = "right"),1),
         recent_avg_winpercent40 = lag(rollmean(feedback_dich, 40, na.pad = TRUE, align = "right"),1))

ggplot(file_timecourse%>%filter(participant_ID == 1, blockLoop_thisRepN == 4), aes(x = trialLoop_thisRepN))+
  stat_summary(aes(y = recent_avg_winpercent1), color = "grey", geom = "line",size=2)+
  stat_summary(aes(y = recent_avg_winpercent30), color = "gold", geom = "line",size=2)+
  stat_summary(aes(y = recent_avg_winpercent17), color = "orange", geom = "line",size=2)+
  stat_summary(aes(y = recent_avg_winpercent10), color = "red", geom = "line",size=2)+
  stat_summary(aes(y = recent_avg_winpercent5), color = "red3", geom = "line",size=2)+
  stat_summary(aes(y = recent_avg_winpercent3), color = "brown4", geom = "line",size=2)
```

## skimming through the distribution of raw data
```{r}
ggdensity(file_tbt_raw%>%mutate(trialResp_rt = log(trialResp_rt)), x = "trialResp_rt", rug = TRUE,add = 'median',
   color = "tempo", fill = "tempo")+
  scale_color_brewer(palette="Set2")+
  scale_fill_brewer(palette="Set2")+
  geom_vline(xintercept  = log(0.4))+
  geom_vline(xintercept  = log(0.6))+
  geom_vline(xintercept  = log(1.0))+
  labs(x = 'Response Time',
       y = 'Density (raw data)')

ggdensity(file_tbt_raw%>%mutate(trialResp_rt = (trialResp_rt)), x = "trialResp_rt", rug = TRUE,add = 'median',
   color = "tempo", fill = "tempo")+
  scale_color_brewer(palette="Set2")+
  scale_fill_brewer(palette="Set2")+
  geom_vline(xintercept  = (0.4))+
  geom_vline(xintercept  = (0.6))+
  geom_vline(xintercept  = (1.0))+
  labs(x = 'Response Time',
       y = 'Density (raw data)')

ggdensity(file_tbt_raw, x = "rt_adjustment", rug = TRUE,add = 'median',
   color = "tempo", fill = "tempo")+
  scale_color_brewer(palette="Set2")+
  scale_fill_brewer(palette="Set2")+
  labs(y = 'Density (raw data)')

ggdensity(file_tbt_raw, x = "last_rt_deviance_mean10", rug = TRUE,add = 'median',
   color = "tempo", fill = "tempo")+
  scale_color_brewer(palette="Set2")+
  scale_fill_brewer(palette="Set2")+
  labs(y = 'Density (raw data)')

ggdensity(file_tbt_raw%>%filter(rERPRewp!=-99), x = "rERPRewp", rug = TRUE,add = 'median',
   color = "tempo", fill = "tempo")+
  scale_color_brewer(palette="Set2")+
  scale_fill_brewer(palette="Set2")+
  labs(y = 'Density (raw data)')
```

## excluding 1% outliers on both end (this step flags the outliers in the raw file)
*RT is excluded based on log-transformed values because it is positively skewed.* RT, RT adjustment and RT deviations need to be excluded independently because the latter two are the derivatives of RT and its value depends on the difference between the current and previous RTs.

```{r data cleaning, include=FALSE}
if (exclude_method == "quantile"){
  # rt outliers (needs log transformation because RTs are positively skewed)
  tbt_outlier <-exp(
    c(log(quantile(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "fast")], ci)),
      log(quantile(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "medium")], ci)),
      log(quantile(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "slow")], ci)))
    )

  #RT adjustment outliers
  rtAdj_outlier <-quantile(file_tbt_raw$rt_adjustment, ci,na.rm = TRUE)

  #RT deviation outliers
  rtDev_outlier <-quantile(file_tbt_raw$last_rt_deviance_mean10, ci,na.rm = TRUE)

  # ERP artifacts
  file_tbt_raw$eeg_include = 0
  rtEEG_outlier <- quantile(file_tbt_raw$rERPRewp[which(file_tbt_raw$erpRewp != -99,
                                                        file_tbt_raw$rERPRewp!=-99)], ci,na.rm = TRUE)

  } else if (exclude_method == "std"){ #another exclusion methods
    times = 4
    # rt outlier (log transformation)
  tbt_outlier <-exp(
    c(mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "fast")]))
      -times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "fast")])),
      mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "fast")]))
      +times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "fast")])),
      mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "medium")]))
      -times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "medium")])),
      mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "medium")]))
      +times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "medium")])),
      mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "slow")]))
      -times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "slow")])),
      mean(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "slow")]))
      +times*sd(log(file_tbt_raw$trialResp_rt[which(file_tbt_raw$tempo == "slow")]))
      )
    )
  
  rtAdj_outlier <- c(mean(file_tbt_raw$rt_adjustment,na.rm = TRUE)
                     -times*sd(file_tbt_raw$rt_adjustment,na.rm = TRUE),
                  mean(file_tbt_raw$rt_adjustment,na.rm = TRUE)
                  +times*sd(file_tbt_raw$rt_adjustment,na.rm = TRUE))
   
  #RT deviation outliers
  rtDev_outlier <- c(mean(file_tbt_raw$last_rt_deviance_mean10,na.rm = TRUE)
                     -times*sd(file_tbt_raw$last_rt_deviance_mean10,na.rm = TRUE),
                  mean(file_tbt_raw$last_rt_deviance_mean10,na.rm = TRUE)
                  +times*sd(file_tbt_raw$last_rt_deviance_mean10,na.rm = TRUE))

  # ERP artifacts

  rtEEG_outlier <- c(mean(file_tbt_raw$rERPRewp[which(file_tbt_raw$erpRewp != -99,
                                                        file_tbt_raw$rERPRewp!=-99)],na.rm = TRUE)
                     -times*sd(file_tbt_raw$rERPRewp[which(file_tbt_raw$erpRewp != -99,
                                                        file_tbt_raw$rERPRewp!=-99)],na.rm = TRUE),
                  mean(file_tbt_raw$rERPRewp[which(file_tbt_raw$erpRewp != -99,
                                                        file_tbt_raw$rERPRewp!=-99)],na.rm = TRUE)
                  +times*sd(file_tbt_raw$rERPRewp[which(file_tbt_raw$erpRewp != -99,
                                                        file_tbt_raw$rERPRewp!=-99)],na.rm = TRUE)
                  )
}
```

## exclude the outliers as specified above and print the exclusion rate

```{r}
print(paste0(c("rt lower boundary: ","rt upper boundary: "),tbt_outlier))
print(paste0(c("rt adjustment lower boundary: ","rt adjustment upper boundary: "),rtAdj_outlier))
print(paste0(c("rt deviation lower boundary: ","rt deviation upper boundary: "),rtDev_outlier))
```

## do the actual exclusion based on all the flags
```{r include = FALSE}
file_tbt_raw$rt_include = 0
file_tbt_raw$rt_include[which(file_tbt_raw$tempo == "fast" & 
                                file_tbt_raw$trialResp_rt >= tbt_outlier[1] &
                                file_tbt_raw$trialResp_rt <= tbt_outlier[2] & 
                                file_tbt_raw$trialResp_corr == 1)] <- 1
file_tbt_raw$rt_include[which(file_tbt_raw$tempo == "medium" & 
                                file_tbt_raw$trialResp_rt >= tbt_outlier[3] &
                                file_tbt_raw$trialResp_rt <= tbt_outlier[4] & 
                                file_tbt_raw$trialResp_corr == 1)] <- 1
file_tbt_raw$rt_include[which(file_tbt_raw$tempo == "slow" & 
                                file_tbt_raw$trialResp_rt >= tbt_outlier[5] &
                                file_tbt_raw$trialResp_rt <= tbt_outlier[6] & 
                                file_tbt_raw$trialResp_corr == 1)] <- 1

file_tbt_raw$rtAdj_include = 0
file_tbt_raw$rtAdj_include[which(file_tbt_raw$rt_adjustment >= rtAdj_outlier[1] &
                                     file_tbt_raw$rt_adjustment <= rtAdj_outlier[2])] <- 1

file_tbt_raw$rtDev_include = 0
file_tbt_raw$rtDev_include[which((file_tbt_raw$last_rt_deviance_mean10 >= rtDev_outlier[1] &
                                     file_tbt_raw$last_rt_deviance_mean10 <= rtDev_outlier[2]|file_tbt_raw$trialLoop_thisRepN < 9))] <- 1

file_tbt_raw$eeg_include = 0
file_tbt_raw$eeg_include[which(file_tbt_raw$erpRewp != -99 &
                                 file_tbt_raw$rERPRewp !=-99 &
                                   file_tbt_raw$rERPRewp > rtEEG_outlier[1] & 
                                 file_tbt_raw$rERPRewp < rtEEG_outlier[2])] <- 1
```

```{r}
file_tbt_raw$include <- as.numeric(file_tbt_raw$rt_include == 1 & 
                                     file_tbt_raw$rtAdj_include==1 & 
                                     file_tbt_raw$eeg_include==1 & 
                                     file_tbt_raw$rtDev_include == 1)

count(file_tbt_raw%>%ungroup,include)

print(paste0("Inclusion rate = ",length(which(file_tbt_raw$include == 1))/length(which(file_tbt_raw_orig$rERPRewp != -99))))

print(paste0("Inclusion rate = ",length(which(file_tbt_raw$include == 1))/length(which(file_tbt_raw$rERPRewp != -99))))

file_tbt <- file_tbt_raw%>%filter(include == 1)

range(file_tbt$trialResp_rt,na.rm = TRUE)
range(file_tbt$rt_adjustment,na.rm = TRUE)
range(file_tbt$rERPRewp,na.rm = TRUE)
range(file_tbt$last_rt_deviance_mean10,na.rm = TRUE)

write.csv(file_tbt, "data_files/data_tbt.csv")
```


### exclude for file_timecourse.csv for analysing the timecourse effect
```{r include = FALSE}
file_timecourse$rt_include = 0
file_timecourse$rt_include[which(file_timecourse$tempo == "fast" & file_timecourse$trialResp_rt >= tbt_outlier[1] 
                                 & file_timecourse$trialResp_rt <= tbt_outlier[2] 
                                 & file_timecourse$trialResp_corr == 1)] <- 1
file_timecourse$rt_include[which(file_timecourse$tempo == "medium" 
                                 & file_timecourse$trialResp_rt >= tbt_outlier[3] 
                                 & file_timecourse$trialResp_rt <= tbt_outlier[4] 
                                 & file_timecourse$trialResp_corr == 1)] <- 1
file_timecourse$rt_include[which(file_timecourse$tempo == "slow" 
                                 & file_timecourse$trialResp_rt >= tbt_outlier[5] 
                                 & file_timecourse$trialResp_rt <= tbt_outlier[6] 
                                 & file_timecourse$trialResp_corr == 1)] <- 1

file_timecourse$rtAdj_include = 0
file_timecourse$rtAdj_include[which(file_timecourse$rt_adjustment >= rtAdj_outlier[1] 
                                    & file_timecourse$rt_adjustment <= rtAdj_outlier[2])] <- 1
file_timecourse$rtDev_include[which((file_timecourse$last_rt_deviance_mean10 >= rtDev_outlier[1] 
                                     & file_timecourse$last_rt_deviance_mean10 <= rtDev_outlier[2]|file_tbt_raw$trialLoop_thisRepN < 9))] <- 1

file_timecourse$eeg_include = 0
file_timecourse$eeg_include[which(file_timecourse$erpRewp != -99 
                                  & file_timecourse$rERPRewp !=-99 
                                  & file_timecourse$rERPRewp > rtEEG_outlier[1] 
                                  & file_timecourse$rERPRewp < rtEEG_outlier[2])] <- 1
```

```{r}
file_timecourse$include <- as.numeric(file_timecourse$rt_include == 1 & file_timecourse$rtAdj_include==1 & file_timecourse$eeg_include==1 & file_timecourse$rtDev_include == 1)

count(file_timecourse%>%ungroup,include)

print(paste0("Inclusion rate = ",length(which(file_timecourse$include == 1))/length(which(file_timecourse$rERPRewp != -99))))

file_timecourse_out <- file_timecourse%>%filter(include == 1)

range(file_timecourse_out$trialResp_rt,na.rm = TRUE)
range(file_timecourse_out$rt_adjustment,na.rm = TRUE)
range(file_timecourse_out$rERPRewp,na.rm = TRUE)
range(file_timecourse_out$last_rt_deviance_mean10,na.rm = TRUE)

write.csv(file_timecourse_out, "data_files/data_tbt_timecourse.csv")
```